I wish to first thank my mother, Liria Yuriko, that always supported my decisions. 
She was always my teacher, protector and showed much of all I needed to live my life.
She always accepted me for who I am and continues to do so until today.
I own everything I am to her.
Secondly, I thank my brothers, who helped me and my mother when needed.

I also have to thank Lorena Casarotto, for helping and supporting me during this last 
two years of my masters degree and showing me her clarity of mind even when things were 
not so good, and Fernanda Martins and his mother, Marcia, for everything they did for 
me during my entire undergraduate years.
Moreover, Eduardo Costa also deserves his mention for being a good company and friend 
for almost all of my adult life.
I owe a lot of my experiences to all of them.

In my years as a undergraduate in Universidade Estadual de Maringá, my ex-advisor, 
Anderson Faustino, taught me a lot about research and computer science.
In my masters, I have to thank my advisor, Vinicius Fernandes dos Santos, and co-advisor, 
Sebastián Urrutia, for the encouragement, patience and vast knowledge in their respective 
fields.

Lastly, I have to thank all the professors that were part of my life in some way and 
gave me the necessary knowledge to finish this dissertation. And, of course, to all the 
friends and my psychologist, Luis Mello, that helped me overcome these last difficult years.
I am what I am not because of my accomplishments, but only because of those that raised 
me and helped me learn how to tread my own path in life.
And for all those I did wrong, I am sorry.